Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2020-12-21 GWLDCII.tex
worked on the paragraph we were discussing at the end of the call today

It is worth noting at this point that the \hlfix{combinatorics of the Wilson loop diagrams are different from the combinatorics of the Amplituhedron}{I think we should discuss this paragraph -- it may be misleading in a bad way}, just as the the volume forms associated to the BCFW diagrams are different from those associated to the Wilson Loop diagrams. For instance, the BCFW are most readily related to the geometry of a postive Grassmannian via plabic graphs. Meanwhile, the Wilson loop diagrams correspond to matrices with variable valued entries (see section \ref{section WLD background}) and Grassmann Necklaces (see Algorithm \ref{alg:put GN on WLD}).  These two combinatorial representations of the positive Grassmannians have different strengths and weaknesses, and it is not possible to give a one to one translation of the combinatorial tools used for the Amplituhedron and BCFW diagrams, and the combinatorial tools used for the Wilson loop diagrams, associated matrices and Grassmann Necklaces. For instance, square moves and merge-expand moves give different graphical representations of the same positroid cell. There is no equivalent diagramatical equivalence for Wilson loop diagrams, though it has been shown (see \cite{wilsonloop, generalcombinatoricsI}) that certain classes of diagrams parametrize the same positroid cells. On the other hand, in order to get a parametrization of the associated positroid cell from the plabic graphs, one must assign weights to the vertices and used them to compute Pl\"{u}cker coordinates \cite[Section 11]{Postnikov}, while the Wilson loop diagrams \emph{are} a parametrization of the associated positroid. That is, one can compute the Pl\"{u}cker coordinates directly from the associated matrices.  \sanote{This para is in answer to 1 and 4 of report Y. Should it be moved (in a modified form) to the begining of section 3? Should it be in both places?}

>>>>

The Amplituhedron and the Wilson loop diagrams describe the same physical amplitudes, and via their relation to positroids, they have similar combinatorics, but these combinatorial objects manifest themselves differently in the two cases.  For instance, square moves and merge-expand moves on the plabic graph give different graphical representations of the same positroid cell in the Amplituhedron case, while as we show in our companion paper \cite{generalcombinatoricsI}, retriangulations of polygon dissections associated to Wilson loop diagrams give all the Wilson loop diagrams associated to the same positroid cell.
A direct connection between the geometry of the Amplituhedron and the geometry of the Wilson loop diagrams is also not known.  The geometric spaces in the two situations have different dimensions and \hlfix{examples show}{is this true?} that they do not relate by a coordinate projection or boundary map or other straightforward connection.  The deeper connection, which physics tells us should exist, remains to be uncovered in future work.
\note{This doesn't address the parametrization part yet.}

%It is worth noting at this point that the \hlfix{combinatorics of the Wilson loop diagrams are different from the combinatorics of the Amplituhedron}{I think we should discuss this paragraph -- it may be misleading in a bad way}, just as the the volume forms associated to the BCFW diagrams are different from those associated to the Wilson Loop diagrams. For instance, the BCFW are most readily related to the geometry of a postive Grassmannian via plabic graphs. Meanwhile, the Wilson loop diagrams correspond to matrices with variable valued entries (see section \ref{section WLD background}) and Grassmann Necklaces (see Algorithm \ref{alg:put GN on WLD}).  These two combinatorial representations of the positive Grassmannians have different strengths and weaknesses, and it is not possible to give a one to one translation of the combinatorial tools used for the Amplituhedron and BCFW diagrams, and the combinatorial tools used for the Wilson loop diagrams, associated matrices and Grassmann Necklaces. For instance, square moves and merge-expand moves give different graphical representations of the same positroid cell. There is no equivalent diagramatical equivalence for Wilson loop diagrams, though it has been shown (see \cite{wilsonloop, generalcombinatoricsI}) that certain classes of diagrams parametrize the same positroid cells. On the other hand, in order to get a parametrization of the associated positroid cell from the plabic graphs, one must assign weights to the vertices and used them to compute Pl\"{u}cker coordinates \cite[Section 11]{Postnikov}, while the Wilson loop diagrams \emph{are} a parametrization of the associated positroid. That is, one can compute the Pl\"{u}cker coordinates directly from the associated matrices.  \sanote{This para is in answer to 1 and 4 of report Y. Should it be moved (in a modified form) to the begining of section 3? Should it be in both places?}
